%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{LI Geng} % Your name
\address{https://github.com/anguslee} % Personal websites
\address{(+86)13xxxxxx033 \\ angus.lee8329@gmail.com} % Phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Summary}

\item Good at getting the big picture of projects; capable of basing new products on the sucess of previous ones,
 and making reasonable compromise between software features,
maintainability and project delivery time;
\item Well-grounded knowledge in computing technologies, distributed system analysis and architect,
 and master several programming languages, of which C/C++, Java and Lisp are my best.
\item Trilingural: Chinese (Native), English (Proficient), French (Average)
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Technical Strengths}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%System Analysis and Architect \\
%Programming Languages & C, C++, Java, Lisp \\
%Operating Systems & Linux \\
%\end{tabular}

%\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Qunar, Inc (NASDAQ:QUNR)}{July 2010 - Present}{Senior Software Developing Engineer}{Beijing, CHINA}
\item Bidding advertising system architect, design and project managing;
\item Search engine architect, development and optimization.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{School of EECS, Peking University}{September 2006 - July 2010}{Master Candidate}{Beijing, CHINA}
\item 863 Grant: Ocean Data Information Retrieval
\item Research on the link structure of the Web in mainland China
\item Co-published poster on www2008: A
Teapot Graph and Its Hierarchical Structure of the Chinese Web
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Baidu, Inc (www.baidu.com)}{October 2009 - December 2009}{Intern Software Engineer}{Beijing, CHINA}
\item Participated in the development of storage and computing
  infrastructure for big data.
\end{rSubsection}

\begin{rSubsection}{The Beijing Organizing Committee for the Games of
    the XXIX Olympiad}{July 2007 - September 2008}{Intern}{Beijing, CHINA}
\item Internship in the fencing hall for the 2008 Olympic Games.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{School of EECS, Peking University}{September 2002 - July 2006}{Bachelor Candidate}{Beijing, CHINA}
\item Major in computer science, minor in French.
\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}

\begin{rSubsection}{Bidding Advertising System for Online Products}{Qunar, Inc}{October 2013 - Present}
{Beijing, CHINA}
\item In charge of system architect and design, project management and part of coding.
\item Standardized the development process of cutting in different lines of products to the bidding system.
\item On-time delivery on a tight schedule for the first release.
\end{rSubsection}

\begin{rSubsection}{Web Search Architect Design and Implementation}{Qunar, Inc}{June 2012 - Present}
{Beijing, CHINA}
\item In charge of ranking quality on the list page of package.qunar.com.
\item Tackle performance related issues such as memcached client selection and database connection optimization; Reduce number of active memcached connection to 1 without affecting performance; Idle database connection decreased by some 60\%.
\item Lead and manage projects for new feature development; Project delay dropped to almost 0.

\end{rSubsection}

\begin{rSubsection}{Search Engine Development}{Qunar, Inc}{June 2011 -
    June 2012}{Beijing, CHINA}
\item Developing on top of the open-source Luene search engine, primarily working on the feature of handling search
request distribution to appropriate part of the inverted indices that are run on a cluster of web servers and their
search response merging, with support for automatic failover and load balancing and on-demand role
assignment of search engine nodes.
\item Optimization: Resident memory usage dropped by some 30\% with improved data structure implementations.
\end{rSubsection}

\begin{rSubsection}{Bidding Advertising Search Engine
    Development}{Qunar, Inc}{January 2011 -
    January 2012}{Beijing, CHINA}
\item Design and implement data query engine that handles ranking and efficient retrieval of advertisements.
\item Reduce average latency from 13ms to less than 3ms by a feedback to product manager to discard a useless 
feature based on activity profiling. 
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Peking University, Beijing} \hfill {\em July 2010} \\ 
M.S. in Computer Science And Technology \\
Internship at the Fencing Hall of National Convention Center of BOCOG \\
Head of fencing club of the JING WU society from 2009 to 2010 

{\bf Peking University, Beijing} \hfill {\em July 2006} \\ 
B.S. in Computer Science And Technology \\
Minor in French

\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
