%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{LI Geng} % Your name
\address{https://stackoverflow.com/users/486149/angus-lee} % Personal websites
\address{(+86) 13xxxxxxxxx \\ angus.lee8329@gmail.com} % Phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Summary}

\item Experienced in web server developing, Linux system performance analysis and planning, JVM performance tuning and good with multiple programming languages such as C/C++, Java, Common Lisp, Python and Scala;
\item Experienced tech team manager: up to group of 40 engineers;
\item Trilingual: Chinese (Native), English (Proficient), French (Average)

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Technical Strengths}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%System Analysis and Architect \\
%Programming Languages & C, C++, Java, Lisp \\
%Operating Systems & Linux \\
%\end{tabular}

%\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

  \begin{rSubsection}{OpenResty.com, Inc}{Jul. 2020 - Sep. 2021}{Senior Software Developing Engineer}{Beijing, CHINA}
  \item OpenResty development:
    \begin {itemize}
    \item Support for offloading SSL encryption/decryption to Intel's QAT hardware in HTTPS transimittions.
    \item Nginx QUIC (HTTP3) support.
    \end{itemize}
  \item Design and manage database for time-series data manipulation.
  \end{rSubsection}
  
  \begin{rSubsection}{Qunar, Inc}{Jul. 2010 - Jun. 2020}{Senior Software Developing Engineer}{Beijing, CHINA}
  \item Technical lead for dujia.qunar.com BU
    \begin{itemize}
    \item Search engine architect, development and optimization;
    \item Bidding advertising system architect and design;
    \item Application performance analysis and optimization at JVM and operating system level;
    \item Manage tech team's workflow.
    \end{itemize}
  \item Member of corperation-wide Technology Committee
    \begin{itemize}
    \item Work out corperation-wide promotion guidelines for tech staff on Java and Python development;
    \item Standardize procedures for Java code submission and product release on occassions of risky codes;
    \item Review staff promotion to high levels.
    \end{itemize}
  
  \end{rSubsection}

%------------------------------------------------

  \begin{rSubsection}{Baidu, Inc (www.baidu.com)}{October 2009 - December 2009}{Intern Software Engineer}{Beijing, CHINA}
  \item Participated in the development of storage and computing infrastructure for big data.
  \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Peking University, Beijing} \hfill {\em Jul. 2010} \\ 
M.S. in Computer Science And Technology \\
Internship at the Fencing Hall of National Convention Center of BOCOG \\
Head of fencing club of the JING WU society from 2009 to 2010 

{\bf Peking University, Beijing} \hfill {\em Jul. 2006} \\ 
B.S. in Computer Science And Technology \\
Minor in French

\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
